Methods for Polyphonic Music Transcription

### 2013-12-02 paper/paper.tex
Replaced letter x with 'times' symbol when describing matrix sizes in the non-negative matrix factorization section

Non-negative matrix factorization (NMF) is an unsupervised, dimensionality reduction technique that factors a non-negative matrix $V$ with dimensions $FxN$ into two matrices,

@@

\noindent where $W$ is an $FxK$ matrix and $H$ is a $KxN$ matrix. $K$ is typically chosen so that $F*K + K*N << F*N$.

>>>>

Non-negative matrix factorization (NMF) is an unsupervised, dimensionality reduction technique that factors a non-negative matrix $V$ with dimensions $F \times N$ into two matrices,

@@

\noindent where $W$ is an $F \times K$ matrix and $H$ is a $K \times N$ matrix. $K$ is typically chosen so that $F*K + K*N << F*N$.
